---
title: "Estimating DCMs"
output:
  html_notebook:
    df_print: paged
editor_options: 
  chunk_output_type: inline
---

```{r setup, include = FALSE}
library(measr)
library(dplyr)
library(fs)

taylor_data <- readRDS("data/taylor-data.rds")
taylor_qmatrix <- readRDS("data/taylor-qmatrix.rds")

if (!dir_exists("fits")) dir_create("fits")
```

## Exercise 1

View the MacReady & Dayton (1977) data (`mdm_data` and `mdm_qmatrix`) and the Taylor data (`taylor_data` and `taylor_qmatrix`).

1. How many items are in the data?
2. How many respondents are in the data?
3. How many attributes are measured?

```{r}

```

## Exercise 2

Complete the `parameters` and `transformed parameters` blocks for the MDM data.

```{stan output.var="mdm_lcdm", eval = FALSE}
data {
  int<lower=1> I;           // # of items
  int<lower=1> R;           // # of respondents 
  int<lower=1> A;           // # of attributes
  int<lower=1> C;           // # of attribute profiles (latent classes) 
  matrix[R,I] y;            // response matrix
}
parameters {
  simplex[C] Vc;
  
  // item parameters
  
}
transformed parameters {
  matrix[I,C] PImat;
  
  PImat[1,1] = inv_logit();
  PImat[1,2] = inv_logit();
  PImat[2,1] = inv_logit();
  PImat[2,2] = inv_logit();
  PImat[3,1] = inv_logit();
  PImat[3,2] = inv_logit();
  PImat[4,1] = inv_logit();
  PImat[4,2] = inv_logit();
}
model {
  for (r in 1:R) {
    real ps[C];
    for (c in 1:C) {
      real log_items[I];
      for (i in 1:I) {
        log_items[i] = y[r,i] * log(PImat[i,c]) + (1 - y[r,i]) * log(1 - pi[i,c]);
      }
      ps[c] = log(Vc[c]) + sum(log_items);
    }
    target += log_sum_exp(ps);
  }
}
```

## Exercise 3

Estimate and LCDM on the Taylor data. Your model should have:

* 2 chains
* 1000 warmup and 500 sampling iterations
* Use whichever backend you prefer

```{r}
taylor_lcdm <- measr_dcm(
  data = _____, qmatrix = _____,
  resp_id = _____,
  type = _____,
  method = _____, backend = _____,
  _____,
  file = "fits/taylor-lcdm"
)
```

## Exercise 4

What proportion of respondents have mastered both songwriting and vocals in the Taylor data?

What is the probability that *folklore* has mastered vocals?

```{r}

```

## Exercise 5

Estimate a new LCDM model for the Taylor data with the following priors:

* Intercepts: `normal(-1, 2)`
  * Except item 3, which should use a `normal(0, 1)` prior
* Main effects: `lognormal(0, 1)`

Use `backend = "optim"` for a speedier estimation

Extract the prior to see that the specifications were applied

```{r}
new_taylor <- measr_dcm(
  data = taylor_data, qmatrix = taylor_qmatrix,
  resp_id = "respondent",
  type = "lcdm",
  _____,
  method = "optim", backend = "rstan",
  file = "fits/taylor-new-prior"
)

measr_extract(new_taylor, _____)
```
